All students must submit an electronic PDF version of the written question including plots generated from the codes. We
highly recommend typesetting your solutions via \LaTeX. 
All students must also submit a zip file of
their source code to Gradescope, which should be created using the
\texttt{make\_zip.py} script. You
should make sure to (1) restrict yourself to only using libraries included in
the
\texttt{environment.yml} file, and (2) make sure your code runs without errors.
Your submission may be evaluated by the
auto-grader using a private test set, or used for verifying the outputs reported in the writeup. Please make sure that your PDF file and zip file are submitted to the corresponding Gradescope assignments respectively. We reserve the right to not give any points to the written solutions if the associated code is not submitted.

\vspace{0.1in}
{\bf Honor code:} 
We strongly encourage students to form study groups. Students may discuss and work on homework problems in groups. However, each student must write down the solution independently, and without referring to written notes from the joint session. Each student must understand the solution well enough in order to reconstruct it by him/herself. It is an honor code violation to copy, refer to, or look at written or code solutions from a previous year, including but not limited to: official solutions from a previous year, solutions posted online, and solutions you or someone else may have written up in a previous year. Furthermore, it is an honor code violation to post your assignment solutions online, such as on a public git repo. We run plagiarism-detection software on your code against past solutions as well as student submissions from previous years. Please take the time to familiarize yourself with the Stanford Honor Code\footnote{\hurl{https://communitystandards.stanford.edu/policies-and-guidance/honor-code}} and the Stanford Honor Code\footnote{\hurl{https://web.stanford.edu/class/archive/cs/cs106b/cs106b.1164/handouts/honor-code.pdf}} as it pertains to CS courses.
